---
title: "2018 Lynn Canal MAGMA Run"
date: "01/28/2019"
editor_options:
  chunk_output_type: inline
output:
  html_document:
    df_print: paged
subtitle: 
creator: Chase Jalbert
---

<b> Project Overview </b> 

This is a post-season analysis of Lynn Canal D115 fishery. I want an age-specific stock composition for all major contributing age classes (>5%; 1.2, 1.3, 2.2, 2.3, other) using mark- and age-enhanced genetic mixed-stock analysis (MAGMA).    

For the purposes of this project, I am just concerend about the breakdown by age, across all statweeks, and statareas. I will assign <b>all</b> stat areas as 115-<i>00</i>, since this doesnt exist and is currently how stat area is recorded.    
 
Total season estimates are to be provided by age group. The algorithm will be run for 40 000 repititions, and the first 20 000 repititions will be discarded.    

Deliverables: 
    
    Point estimates, Credibility intervals
    
<b> Script Overview </b>

Now that everything is setup and verified, the model is ready. Briefly, we run 40K repititions, burn the first 20k, and thin by 10, with 5 chains. If there are issues (e.g., no convergence) then we bump up to 80K, 40k, 100, 5, respectively. Here, I have provided both options, so uncomment whatever you need.   

At this point, I will switch the scripts over to our genetics server and make use of some extra processing power.    

<b> Begin MAGMA Run </b>

Start with a 40K run: 

```{r MAGMA40K}
wd <- "C:/Analysis/MAGMA/LynnCanalPost_2018" # This must have three subdirectories, 1) analysis, 2) data, 3) output which contain the input files obtained by running MAGMA scripts 1 - 2. MAGMA will output to the 'output' directory

setwd(wd)

source("analysis/magma.R") # source the magma function

magma(nreps = 40000, burn = 20000, thin = 10, nchains = 5, wd = wd) # run MAGMA
```

The run was stated on: xx/xx/xxxx at xxxx
The run was completed on: xx/xx/xxxx at xxxx
The total time was: xx

OR CAN RUN AT 80K, if necessary... 

```{r MAGMA80K}
# wd <- "V:/Analysis/1_SEAK/Sockeye/Mixture/Lynn Canal Postseason/2018/MAGMA/" # This must have three subdirectories, 1) analysis, 2) data, 3) output and they must contain the files obtained by running the setup above (Parts 1 - 3)
# 
# setwd(wd)
# 
# source("analysis/magma.R") # source the magma function
# 
# magma(nreps = 80000, burn = 40000, thin = 100, nchains = 5, wd = wd) # run MAGMA
```

The run was stated on: xx/xx/xxxx at xxxx
The run was completed on: xx/xx/xxxx at xxxx
The total time was: xx

Once the run finishes move onto the next script "4-D115_MAGMA_summary.Rmd" to tidy up the output, check out convergence, and create summary reports.    

In the spirit of record keeping:
```{r sessioninfo}
sessionInfo()
```

