---
title: "2018 Lynn Canal MAGMA Summary"
date: "01/25/2019"
editor_options:
  chunk_output_type: inline
output:
  html_document:
    df_print: paged
subtitle: 
creator: Chase Jalbert
---

This script takes the MAGMA output and creates summary files along with a summary workspace (RData). Essentially it works through each chain and compiles necessary statistics presenting them into a 

```{r setup, include = FALSE}
# This forces the working directory for ALL chunks in the notebook. Note that it must be run first, in the "setup" chunk or it will fail. 
wd <-
  "V:/Analysis/1_SEAK/Sockeye/Mixture/Lynn Canal Postseason/2018/MAGMA/"

knitr::opts_knit$set(root.dir = wd)

```


```{r arguments}
args <-
  dget("output/MAGMA_arguments.txt")  # This will get a list with the arguments used when magma.R was run, need to set wd first

invisible(sapply(names(args)[1:4], function(arg) {
  assign(x = arg, value = args[[arg]], pos = 1)
}))  # This will load "nreps", "burn", "thin", and "nchains" to the workspace

nreps

burn

thin

nchains

alpha <- 0.10

zero <-
  "halfafish" #  This uses half a fish as the threshold for zero (based on harvest). Otherwise can be set as a numeric e.g. zero = 5e-7.

#  age_class <- new_age_class # You can re-specify this argument if u want to summarise ages withe respect to a different "age_class" vector.

groups <-
  read.table("data/groups.txt", header = TRUE, row.names = 1)

group_names <- read.table("data/group_names.txt", header = TRUE)
```

First, compile and create the MAGMA summary workspace. 
```{r magma_summary}
startTime <- Sys.time()


packages <- c("reshape", "coda", "readr")

invisible( sapply( packages, function(pkg)
  while (!require( pkg, character.only = TRUE))
    install.packages(
      pkg,
      repos = c("http://rstudio.org/_packages", "http://cran.rstudio.com")
    )))

colsum <-
  function(x, group, reorder = TRUE, ...)
    t(rowsum(t(x), group = group, reorder = reorder, ...))

#setwd(wd)

load("analysis/magma_data.RData")

# print(magma_data_names)

#  c("harvest", "wildpops", "hatcheries", "age_classes", "age_class", "years2run", "districts", "subdistricts", "stat_weeks", "K", "H", "A", "C", "T", "D", "S", "W")

harvest = sort_df(merge(harvest, Reduce(rbind, lapply(seq(
  D
), function(d) {
  grd = expand.grid(
    YEAR = seq(T),
    DISTRICT = d,
    SUBDISTRICT = seq(S[d]),
    STAT_WEEK = seq(W),
    stringsAsFactors = FALSE
  )
  sort_df(grd, vars = c("SUBDISTRICT", "STAT_WEEK"))
})), all = TRUE))

h <-
  tapply(harvest[, ncol(harvest)], harvest[,-ncol(harvest)], c)

n <-
  tapply(metadat$i, metadat[,-c(ncol(metadat) - 1, ncol(metadat))], length)

n[is.na(n)] <- h[is.na(h)] <- 0

paths <-
  lapply(seq(T), function(t) {
    lapply(seq(D), function(d) {
      lapply(seq(S[d]), function(s) {
        lapply(seq(W), function(w) {
          paste0("output/",
                 years2run[t],
                 "/D",
                 districts[d],
                 "/S",
                 subdistricts[[d]][s],
                 "/StatWeek",
                 w)
        })
      })
    })
  })



output <-
  lapply(seq(T), function(t) {
    lapply(seq(D), function(d) {
      lapply(seq(S[d]), function(s) {
        lapply(seq(W), function(w) {
          lapply(seq(nchains), function(chain) {
            rowgroup <-
              factor(paste0(
                rep(group_names[groups[, d], d], times = (nreps - burn) / thin),
                rep(seq(burn + thin, nreps, by = thin), each = K + H)
              ),
              
              levels = paste0(group_names[, d][!is.na(group_names[, d])], rep(
                seq(burn + thin, nreps, by = thin),
                each = length(group_names[, d][!is.na(group_names[, d])])
              )))
            
            file <-
              paste0(paths[[t]][[d]][[s]][[w]], "/PiP", t, d, s, w, "_Chain", chain, ".csv")
            
            
            (n[t, d, s, w] > 0) * h[t, d, s, w] * rowsum(
              colsum(
                suppressMessages(read_csv(
                  file = file, progress = FALSE
                )),
                group = factor(age_classes[age_class], levels = age_classes),
                reorder = FALSE
              ),
              group = rowgroup,
              reorder = FALSE
            )[levels(rowgroup), age_classes]
            
          })
        })
      })
    })
  })

endTime <- Sys.time()

print(endTime - startTime)

save.image("V:/Analysis/1_SEAK/Sockeye/Mixture/Lynn Canal Postseason/2018/MAGMA/output/D115summary40K.RData")
```


#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
###  ages & subdistricts combined by statweek

```{r}
  R <- lapply(seq(T), function(t){ lapply(seq(D), function(d){ lapply(seq(W), function(w){ as.mcmc.list(lapply(seq(nchains), function(chain){ mcmc(Reduce("+", lapply(seq(S[d]), function(s){

           INDEX <- factor(rep(group_names[!is.na(group_names[, d]), d], times = (nreps - burn) / thin), group_names[!is.na(group_names[, d]), d])

           xx = Reduce(cbind, tapply(apply(output[[t]][[d]][[s]][[w]][[chain]], 1, sum), INDEX = INDEX, c, simplify = FALSE))

           dimnames(xx) <- list(paste0("rep", seq(burn + thin, nreps, by = thin)), levels(INDEX))

           xx / max(1, sum((n[t, d, , w] > 0) * h[t, d, , w]))

         }))) })) }) }) })

  R_statweek <- Reduce(rbind, lapply(seq(T), function(t){ Reduce(rbind, lapply(seq(D), function(d){ Reduce(rbind, lapply(seq(W), function(w){

                  zero <- ifelse(is.numeric(zero), zero, 0.5 / max(1, sum((n[t, d, , w] > 0) * h[t, d, , w])))

                  P0 <- apply(apply(Reduce(rbind, R[[t]][[d]][[w]]), 2, "<", value = zero), 2, mean)

                  smmry <- Reduce(cbind, summary(R[[t]][[d]][[w]], quantiles = c(alpha / 2, 1 - alpha / 2)))[, c(1, 2, 5, 6)]

                  GR <- gelman.diag(R[[t]][[d]][[w]], autoburnin = FALSE, multivariate = FALSE)[[1]][, 1]

                  group = group_names[!is.na(group_names[, d]), d]

                  suppressWarnings(data.frame(group = group_names[!is.na(group_names[, d]), d], year = years2run[t], district = districts[d], subdistrict = "all", statweek = stat_weeks[w], smmry, GR = GR, P0 = P0, stringsAsFactors = FALSE))                

                })) })) }))

```

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
###  ages & statweeks combined by subdistrict

  R <- lapply(seq(T), function(t){ lapply(seq(D), function(d){ lapply(seq(S[d]), function(s){ as.mcmc.list(lapply(seq(nchains), function(chain){ mcmc(Reduce("+", lapply(seq(W), function(w){

           INDEX <- factor(rep(group_names[!is.na(group_names[, d]), d], times = (nreps - burn) / thin), group_names[!is.na(group_names[, d]), d])

           xx = Reduce(cbind, tapply(apply(output[[t]][[d]][[s]][[w]][[chain]], 1, sum), INDEX = INDEX, c, simplify = FALSE))

           dimnames(xx) <- list(paste0("rep", seq(burn + thin, nreps, by = thin)), levels(INDEX))

           xx / max(1, sum((n[t, d, s, ] > 0) * h[t, d, s, ]))

         }))) })) }) }) })

  R_subdistrict <- Reduce(rbind, lapply(seq(T), function(t){ Reduce(rbind, lapply(seq(D), function(d){ Reduce(rbind, lapply(seq(S[d]), function(s){

                  zero <- ifelse(is.numeric(zero), zero, 0.5 / max(1, sum((n[t, d, s, ] > 0) * h[t, d, s, ])))

                  P0 <- apply(apply(Reduce(rbind, R[[t]][[d]][[s]]), 2, "<", value = zero), 2, mean)

                  smmry <- Reduce(cbind, summary(R[[t]][[d]][[s]], quantiles = c(alpha / 2, 1 - alpha / 2)))[, c(1, 2, 5, 6)]

                  GR <- gelman.diag(R[[t]][[d]][[s]], autoburnin = FALSE, multivariate = FALSE)[[1]][, 1]

                  suppressWarnings(data.frame(group = group_names[!is.na(group_names[, d]), d], year = years2run[t], district = districts[d], subdistrict = subdistricts[[d]][s], statweek = "all", smmry, GR = GR, P0 = P0, stringsAsFactors = FALSE))                

                })) })) }))

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
### ages, subdistricts and Stat Weeks Combined by district

  R <- lapply(seq(T), function(t){ lapply(seq(D), function(d){ as.mcmc.list(lapply(seq(nchains), function(chain){ mcmc(Reduce("+", lapply(seq(S[d]), function(s){Reduce("+", lapply(seq(W), function(w){

           INDEX <- factor(rep(group_names[!is.na(group_names[, d]), d], times = (nreps - burn) / thin), group_names[!is.na(group_names[, d]), d])

           xx = Reduce(cbind, tapply(apply(output[[t]][[d]][[s]][[w]][[chain]], 1, sum), INDEX = INDEX, c, simplify = FALSE))

           dimnames(xx) <- list(paste0("rep", seq(burn + thin, nreps, by = thin)), levels(INDEX))

           xx / max(1, sum((n[t, d, , ] > 0) * h[t, d, , ]))

         })) }))) })) }) })

  R_district <- Reduce(rbind, lapply(seq(T), function(t){ Reduce(rbind, lapply(seq(D), function(d){

                  zero <- ifelse(is.numeric(zero), zero, 0.5 / max(1, sum((n[t, d, , ] > 0) * h[t, d, , ])))

                  P0 <- apply(apply(Reduce(rbind, R[[t]][[d]]), 2, "<", value = zero), 2, mean)

                  smmry <- Reduce(cbind, summary(R[[t]][[d]], quantiles = c(alpha / 2, 1 - alpha / 2)))[, c(1, 2, 5, 6)]

                  GR <- gelman.diag(R[[t]][[d]], autoburnin = FALSE, multivariate = FALSE)[[1]][, 1]

                  suppressWarnings(data.frame(group = group_names[!is.na(group_names[, d]), d], year = years2run[t], district = districts[d], subdistrict = "all", statweek = "all", smmry, GR = GR, P0 = P0, stringsAsFactors = FALSE))                

                })) })) 

  
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
###  ages combined by subdistrict & statweeks 
  
  R <- lapply(seq(T), function(t){ lapply(seq(D), function(d){ lapply(seq(S[d]), function(s){ lapply(seq(W), function(w){ as.mcmc.list(lapply(seq(nchains), function(chain){  
    
    INDEX <- factor(rep(group_names[!is.na(group_names[, d]), d], times = (nreps - burn) / thin), group_names[!is.na(group_names[, d]), d])
    
    xx = Reduce(cbind, tapply(apply(output[[t]][[d]][[s]][[w]][[chain]], 1, sum), INDEX = INDEX, c, simplify = FALSE))
    
    dimnames(xx) <- list(paste0("rep", seq(burn + thin, nreps, by = thin)), levels(INDEX))
    
    mcmc(xx / max(1, sum((n[t, d, s, w] > 0) * h[t, d, s, w])))
    
  })) }) }) }) })
  
  R_subdistrict_statweek <- Reduce(rbind, lapply(seq(T), function(t){ Reduce(rbind, lapply(seq(D), function(d){ Reduce(rbind, lapply(seq(S[d]), function(s){ Reduce(rbind, lapply(seq(W), function(w){
    
    zero <- ifelse(is.numeric(zero), zero, 0.5 / max(1, sum((n[t, d, s, w] > 0) * h[t, d, s, w])))
    
    P0 <- apply(apply(Reduce(rbind, R[[t]][[d]][[s]][[w]]), 2, "<", value = zero), 2, mean)
    
    smmry <- Reduce(cbind, summary(R[[t]][[d]][[s]][[w]], quantiles = c(alpha / 2, 1 - alpha / 2)))[, c(1, 2, 5, 6)]
    
    GR <- gelman.diag(R[[t]][[d]][[s]][[w]], autoburnin = FALSE, multivariate = FALSE)[[1]][, 1]
    
    suppressWarnings(data.frame(group = group_names[!is.na(group_names[, d]), d], year = years2run[t], district = districts[d], subdistrict = subdistricts[[d]][s], statweek = stat_weeks[w], smmry, GR = GR, P0 = P0, stringsAsFactors = FALSE))                
    
  })) })) })) }))

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
### subdistricts and Stat Weeks Combined by district and age

  PiR <- lapply(seq(T), function(t){ lapply(seq(D), function(d){ as.mcmc.list(lapply(seq(nchains), function(chain){ mcmc(Reduce("+", lapply(seq(S[d]), function(s){Reduce("+", lapply(seq(W), function(w){

           INDEX <- factor(rep(group_names[!is.na(group_names[, d]), d], times = (nreps - burn) / thin), group_names[!is.na(group_names[, d]), d])

           xx = Reduce(cbind, by(output[[t]][[d]][[s]][[w]][[chain]], FUN = cbind, INDICES = INDEX))

           dimnames(xx) <- list(paste0("rep", seq(burn + thin, nreps, by = thin)), paste(rep(levels(INDEX), each = length(age_classes)), rep(age_classes, times = length(levels(INDEX))), sep = "_"))

           xx / max(1, sum((n[t, d, , ] > 0) * h[t, d, , ]))

         })) }))) })) }) })

  PiR_district <- Reduce(rbind, lapply(seq(T), function(t){ Reduce(rbind, lapply(seq(D), function(d){

                  zero <- ifelse(is.numeric(zero), zero, 0.5 / max(1, sum((n[t, d, , ] > 0) * h[t, d, , ])))

                  P0 <- apply(apply(Reduce(rbind, PiR[[t]][[d]]), 2, "<", value = zero), 2, mean)

                  smmry <- Reduce(cbind, summary(PiR[[t]][[d]], quantiles = c(alpha / 2, 1 - alpha / 2)))[, c(1, 2, 5, 6)]

                  GR <- gelman.diag(PiR[[t]][[d]], autoburnin = FALSE, multivariate = FALSE)[[1]][, 1]

                  group <-  rep(group_names[!is.na(group_names[, d]), d], each = length(age_classes))
                  
                  age <- rep(age_classes, times = sum(!is.na(group_names[, d])))

                  suppressWarnings(data.frame(group = group, age = age, year = years2run[t], district = districts[d], subdistrict = "all", statweek = "all", smmry, GR = GR, P0 = P0, stringsAsFactors = FALSE))                

                })) }))

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
### Stat Weeks Combined by subdistrict and age

  PiR <- lapply(seq(T), function(t){ lapply(seq(D), function(d){ lapply(seq(S[d]), function(s){ as.mcmc.list(lapply(seq(nchains), function(chain){ mcmc(Reduce("+", lapply(seq(W), function(w){
    
    INDEX <- factor(rep(group_names[!is.na(group_names[, d]), d], times = (nreps - burn) / thin), group_names[!is.na(group_names[, d]), d])
    
    xx = Reduce(cbind, by(output[[t]][[d]][[s]][[w]][[chain]], FUN = cbind, INDICES = INDEX))
    
    dimnames(xx) <- list(paste0("rep", seq(burn + thin, nreps, by = thin)), paste(rep(levels(INDEX), each = length(age_classes)), rep(age_classes, times = length(levels(INDEX))), sep = "_"))
    
    xx / max(1, sum((n[t, d, s, ] > 0) * h[t, d, s, ]))
    
  }))) })) }) }) })
  
  PiR_subdistrict <- Reduce(rbind, lapply(seq(T), function(t){ Reduce(rbind, lapply(seq(D), function(d){ Reduce(rbind, lapply(seq(S[d]), function(s){
    
    zero <- ifelse(is.numeric(zero), zero, 0.5 / max(1, sum((n[t, d, s, ] > 0) * h[t, d, s, ])))
    
    P0 <- apply(apply(Reduce(rbind, PiR[[t]][[d]][[s]]), 2, "<", value = zero), 2, mean)
    
    smmry <- Reduce(cbind, summary(PiR[[t]][[d]][[s]], quantiles = c(alpha / 2, 1 - alpha / 2)))[, c(1, 2, 5, 6)]
    
    GR <- gelman.diag(PiR[[t]][[d]][[s]], autoburnin = FALSE, multivariate = FALSE)[[1]][, 1]
    
    group <-  rep(group_names[!is.na(group_names[, d]), d], each = length(age_classes))
    
    age <- rep(age_classes, times = sum(!is.na(group_names[, d])))
    
    suppressWarnings(data.frame(group = group, age = age, year = years2run[t], district = districts[d], subdistrict = subdistricts[[d]][s], statweek = "all", smmry, GR = GR, P0 = P0, stringsAsFactors = FALSE))                
    
  })) })) }))
  
  
  
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  write.table(Reduce(rbind, list(R_statweek = R_statweek, R_subdistrict = R_subdistrict, R_district = R_district, R_subdistrict_statweek = R_subdistrict_statweek)), "output/magma_summariesNonagesGroups.txt", row.names = TRUE, col.names = NA, quote = FALSE)
  
  write.table(Reduce(rbind, list(PiR_subdistrict = PiR_subdistrict, PiR_district = PiR_district)), "output/magma_summariesAgesGroups.txt", row.names = TRUE, col.names = NA, quote = FALSE)
  
  # Getting samples sizes
  ntab <- as.data.frame.table(x = tapply(metadat$i, metadat[, -c(ncol(metadat) - 1, ncol(metadat))], length), responseName = "n_total")
  
  ntab <- merge(x = ntab, y = as.data.frame.table(tapply(colsum(x, group = c(rep(1, sum(nalleles)), rep(2, T * C)))[, 1] != 0 & is.na(metadat$i), metadat[, -c(ncol(metadat) - 1, ncol(metadat))], sum), responseName = "wild_genetics"))
  
  ntab <- merge(x = ntab, y = as.data.frame.table(tapply(colsum(x, group = c(rep(1, sum(nalleles)), rep(2, T * C)))[, 1] == 0 & is.na(metadat$i), metadat[, -c(ncol(metadat) - 1, ncol(metadat))], sum), responseName = "wild_no_genetics"))
  
  ntab <- merge(x = ntab, y = as.data.frame.table(tapply(!is.na(metadat$i), metadat[, -c(ncol(metadat) - 1, ncol(metadat))], sum), responseName = "non_wild"))
  
  ntab$w <- factor(ntab$w, seq(W)) 
  
  harvest$STAT_WEEK <- factor(harvest$STAT_WEEK, seq(W))
  
  colnames(ntab)[seq(ncol(harvest) - 1)] <- colnames(harvest)[seq(ncol(harvest) - 1)]
  
  nhtab <- sort_df(merge(ntab, harvest)) 
 
   nhtab[is.na(nhtab)] <- 0 
   
   write.csv(nhtab, "output/sample_size_&_harvest_table.csv")  # this was changed from: write.csv(nhtab, "output/sample_size_&_harvest_tableNB.csv")
   # for compatibility with later scripts. I think this was a copy / paste issue on GEN3. 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Modifying selected districts to allow for combining stat weeks
   
# D108 combined ages, subdistricts, & statweeks 32-34 

   t <- 1   # = match("2018", years2run)
   
   d <- 2   # = match("108", districts)
   
   my_statweeks <- match(c("32","33", "34"), stat_weeks)
   
   R <- as.mcmc.list(lapply(seq(nchains), function(chain){ mcmc(Reduce("+", lapply(seq(S[d]), function(s){ Reduce("+", lapply(my_statweeks, function(w){
     
     Reduce(cbind, tapply(apply(output[[t]][[d]][[s]][[w]][[chain]], 1, sum), INDEX = factor(rep(na.omit(group_names[, d]), times = (nreps - burn) / thin), na.omit(group_names[,d])), c, simplify = FALSE)) 
     
   })) })) / sum((!!n[t, d, , my_statweeks]) * h[t, d, , my_statweeks]))  }))
   
   
   
   R108_32_33_34 <- data.frame(year = years2run[t], district = districts[d], subdistrict = "all", statweek = paste(my_statweeks, collapse = ","), 
                               
                               Reduce(cbind, summary(R, quantiles = c(alpha / 2, 1 - alpha / 2)))[, c(1, 2, 5, 6)], 
                               
                               GR = gelman.diag(R, autoburnin = FALSE, multivariate = FALSE)[[1]][, 1], 
                               
                               P0 =  apply(apply(Reduce(rbind, R), 2, "<", value = 0.5 / sum((!!n[t, d, , my_statweeks]) * h[t, d, , my_statweeks])), 2, mean),  
                               
                               row.names = na.omit(group_names[, d]), stringsAsFactors = FALSE)                
   
   write.table(Reduce(rbind, list(R108_32_33_34 = R108_32_33_34)), "output/D8_weeksModified.txt", row.names = TRUE, col.names = NA, quote = FALSE)
   
   
   #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
   
   # D111 combined ages, subdistricts, & statweeks 32-33 
   
   t <- 1   # = match("2018", years2run)
   
   d <- 3   # = match("111", districts)
   
   my_statweeks <- match(c("32","33"), stat_weeks)
   
   R <- as.mcmc.list(lapply(seq(nchains), function(chain){ mcmc(Reduce("+", lapply(seq(S[d]), function(s){ Reduce("+", lapply(my_statweeks, function(w){
     
     Reduce(cbind, tapply(apply(output[[t]][[d]][[s]][[w]][[chain]], 1, sum), INDEX = factor(rep(na.omit(group_names[, d]), times = (nreps - burn) / thin), na.omit(group_names[,d])), c, simplify = FALSE)) 
     
   })) })) / sum((!!n[t, d, , my_statweeks]) * h[t, d, , my_statweeks]))  }))
   
   
   
   R111_32_33 <- data.frame(year = years2run[t], district = districts[d], subdistrict = "all", statweek = paste(my_statweeks, collapse = ","), 
                               
                               Reduce(cbind, summary(R, quantiles = c(alpha / 2, 1 - alpha / 2)))[, c(1, 2, 5, 6)], 
                               
                               GR = gelman.diag(R, autoburnin = FALSE, multivariate = FALSE)[[1]][, 1], 
                               
                               P0 =  apply(apply(Reduce(rbind, R), 2, "<", value = 0.5 / sum((!!n[t, d, , my_statweeks]) * h[t, d, , my_statweeks])), 2, mean),  
                               
                               row.names = na.omit(group_names[, d]), stringsAsFactors = FALSE)                
   
   
   
   #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
   
   write.table(Reduce(rbind, list(R111_32_33 = R111_32_33)), "output/D11_weeksModified.txt", row.names = TRUE, col.names = NA, quote = FALSE)
   
   #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
   ## adjusting to combine weeks 26 and 28 to create an estimate for sw27 D10641
   
   t <- 1   # = match("2018, years2run)
   
   d <- 1  # = match("106", districts)
   
   s <- match(c("41"), subdistricts[[d]])
   
   my_statweeks <- match(c("26", "28"), stat_weeks)
   
   R <- as.mcmc.list(lapply(seq(nchains), function(chain){ mcmc(Reduce("+", lapply(my_statweeks, function(w){
     
     Reduce(cbind, tapply(apply(output[[t]][[d]][[s]][[w]][[chain]], 1, sum), INDEX = factor(rep(na.omit(group_names[, d]), times = (nreps - burn) / thin), na.omit(group_names[,d])), c, simplify = FALSE)) 
     
   })) / sum((!!n[t, d, s, my_statweeks]) * h[t, d, s, my_statweeks]))  }))
   
   
   
   R10641_26_28 <- data.frame(year = years2run[t], district = districts[d], subdistrict = subdistricts[[d]][s], statweek = paste(my_statweeks, collapse = ","), 
                               
                               Reduce(cbind, summary(R, quantiles = c(alpha / 2, 1 - alpha / 2)))[, c(1, 2, 5, 6)], 
                               
                               GR = gelman.diag(R, autoburnin = FALSE, multivariate = FALSE)[[1]][, 1], 
                               
                               P0 =  apply(apply(Reduce(rbind, R), 2, "<", value = 0.5 / sum((!!n[t, d, s, my_statweeks]) * h[t, d, s, my_statweeks])), 2, mean),  
                               
                               row.names = na.omit(group_names[, d]), stringsAsFactors = FALSE)  
   
   write.table(Reduce(rbind, list(R10641_26_28 = R10641_26_28)), "output/D10641_weeksModified.txt", row.names = TRUE, col.names = NA, quote = FALSE)
   
   