---
title: "Lynn Canal 2019 Postseason Stock Comp by SW"
output:
  html_notebook:
    theme: united
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
```

# Background

Nicole Zeiser called Kyle on 11/27/19 to ask if the summary plots from Lynn Canal Inseason (stacked bar by week) were "final". They are not, because we re-ran all of D115 with MAGMA to get stock by age estimates for the run reconstruction. The **goal** here is to read in the MAGMA output by stat week and recreate the same stacked bar plot of stock comp means.

# Read Objects

Need color and reporting group objects.
```{r}
LynnCanal_groups7 <- dget("../../Lynn Canal Inseason/2019/Objects/LynnCanal_groups7.txt")
LynnCanalColors7 <- dget("../../Lynn Canal Inseason/2019/Objects/LynnCanalColors7.txt")
```

# Read Data

There were multiple MAGMA runs, but Chase indicated that the final run was "80K_03to23"
```{r}
(stock_comp <- read_csv("../2019/MAGMA/output/80k_03to23/NonAges_by_sw_LYNN.csv"))
```

```{r}
stock_comp %>% 
  filter(subdistrict == "all" & StatWeek != "all") %>% 
  mutate(StatWeek = as.numeric(StatWeek)) %>% 
  mutate(ReportingGroup = factor(x = ReportingGroup, levels = LynnCanal_groups7))
```

```{r}
(inseason_stock_comp <- read_csv("../2019/MAGMA/output/80k_03to23/inseason_groups/summaries/NonAges_by_sw_LYNNinseason.csv"))
```

```{r}
inseason_stock_comp %>% 
  filter(subdistrict == "all" & StatWeek != "all") %>% 
  mutate(StatWeek = as.numeric(StatWeek)) %>% 
  mutate(ReportingGroup = factor(x = ReportingGroup, levels = LynnCanal_groups7))
```

Make "inseason" type figure (note that we combined SW 25 and 26 for inseason)
```{r fig.width=10}
inseason_stock_comp %>% 
  filter(subdistrict == "all" & StatWeek != "all") %>% 
  mutate(StatWeek = as.numeric(StatWeek)) %>% 
  mutate(ReportingGroup = factor(x = ReportingGroup, levels = LynnCanal_groups7)) %>% 
  ggplot(aes(x = StatWeek, y = Mean * 100, fill = ReportingGroup)) +
  geom_col(position = "stack", colour = "black") +
  scale_fill_manual(values = LynnCanalColors7) +
  scale_y_continuous(breaks = seq(0, 100, 20), limits = c(0, 100.1), expand = c(0, 0)) +
  scale_x_continuous(breaks = 25:35) +
  ggtitle("Comparison of Weekly Stock\nComposition Estimates") +
  ylab("Stock Composition Estimates (%)") +
  xlab("Stat Week") +
  theme_classic(base_size = 18) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "right")

ggsave(filename = "D115_sw_estimates_2019.png", path = "../2019/Updates/")
```

Save mean estimates by stat week as .csv so she can multiple by harvest.
```{r}
inseason_stock_comp %>% 
  filter(subdistrict == "all" & StatWeek != "all") %>% 
  mutate(StatWeek = as.numeric(StatWeek)) %>% 
  mutate(ReportingGroup = factor(x = ReportingGroup, levels = LynnCanal_groups7)) %>% 
  select(District, ReportingGroup, StatWeek, Mean) %>% 
  spread(ReportingGroup, Mean) %>% 
  write_csv(path = "../2019/Updates/D115_sw_estimates_2019.csv")
```

