---
title: "2018 Lynn Canal MAGMA workspace"
date: "01/22/2019"
editor_options:
  chunk_output_type: inline
output:
  html_document:
    df_print: paged
subtitle: 
creator: Chase Jalbert
---


This notebook sets up the MAGMA workspace. The mnain function is to run the magma_data.R function. The required inputs are:
    
    wd
    loci_name = "loci"
    wildpops_name = "OrderedPops"
    years2run = 2018
    age_classes = c("12", "13", "22", "23", "not")
    
Previously, MAGMA was created and used for TBR only. Now, we are expanding so the function was fixed and some hard-coded flags removed allowwing for more versatility. This means that you will be required to enter ALL inputs, at all times. 

```{r}
source("data/magma_data.R")

magma_data(wd = "V:/Analysis/1_SEAK/Sockeye/Mixture/Lynn Canal Postseason/2018/MAGMA/", loci_name = "loci", wildpops_name = "OrderedPops", years2run = 2018, age_classes = c("12", "13", "22", "23", "not")) 

load("../MAGMA/analysis/magma_data.RData")
```


### Double Checking ###

This is old and simply serves to double check work done in excel, can likely be deleted. 
```{r}
# Getting sample sizes
# District totals
sum(metadat$d == "1") # 3410

## Total number of wild samples
sum(is.na(metadat$i)) # 3410

require(reshape)

colsum <- function(x, group, reorder = TRUE, ...) t(rowsum(t(x), group = group, reorder = reorder, ...))

ntab <- as.data.frame.table(x = tapply(metadat$i, metadat[, -c(ncol(metadat) - 1, ncol(metadat))], length), responseName = "n_total")

ntab <- merge(x = ntab, y = as.data.frame.table(tapply(colsum(x, group = c(rep(1, sum(nalleles)), rep(2, T * C)))[, 1] != 0 & is.na(metadat$i), metadat[, -c(ncol(metadat) - 1, ncol(metadat))], sum), responseName = "wild_genetics"))

ntab <- merge(x = ntab, y = as.data.frame.table(tapply(colsum(x, group = c(rep(1, sum(nalleles)), rep(2, T * C)))[, 1] == 0 & is.na(metadat$i), metadat[, -c(ncol(metadat) - 1, ncol(metadat))], sum), responseName = "wild_no_genetics"))

ntab <- merge(x = ntab, y = as.data.frame.table(tapply(!is.na(metadat$i), metadat[, -c(ncol(metadat) - 1, ncol(metadat))], sum), responseName = "non_wild"))

ntab$w <- factor(ntab$w, seq(W)) 

harvest$STAT_WEEK <- factor(harvest$STAT_WEEK, seq(W))

colnames(ntab)[seq(ncol(harvest) - 1)] <- colnames(harvest)[seq(ncol(harvest) - 1)]

nhtab <- sort_df(merge(ntab, harvest)) 

nhtab[is.na(nhtab)] <- 0
```



