---
title: "2018 Lynn Canal MAGMA Baseline Setup"
date: "01/22/2019"
editor_options:
  chunk_output_type: inline
output:
  html_document:
    df_print: paged
subtitle: 
creator: Chase Jalbert
---


```{r libraries, message = FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman) # install pacman, if not installed
  p_load(tidyverse) # use pacman to load or install+load necessary packages

source("C:/R/function_gcl.r")
```

There was a substaintial baseline update in 2018 so I am re-working this setup script to accomodate the changes. For details see README by Kyle Shedd in the 2018 Lynn Canal Inseason folder.    

I will rely on the "Lynn Canal Inseason 7 Reporting Groups 239 Poupluations 2018.csv" located within that folder for pop, group, and silly vecs.    

Also, I am only interested in 4 groups:    
    
    c("Other", "ChilkatLake", "ChilkatMain", "Chilkoot") 

Anything that is NOT in "ChilkatLake", "ChilkatMain", or "Chilkoot" will be grouped into "Other" for these analyses. 

```{r locus_setup, echo = FASLE}
username = "csjalbert"
.password = "esox.1234"
```


```{r locus_control}
rm(LocusControl) # make sure no old LocusControl

CreateLocusControl.GCL(markersuite = "LynnCanal_PostSeason48loci", username = username, password = .password) # make new Locus control
```

```{r locus_setup}
groups7_pops239 <-
  read_csv(file = "../../Lynn Canal Inseason/2018/Lynn Canal Inseason 7 Reporting Groups 239 Poupluations 2018.csv") # load in updated baseline info


(unique(groups7_pops239$Reporting.Group.New)) # view current reporting groups.


groups4_pops239 <- groups7_pops239 %>%
  mutate(
    GROUPS = case_when(
      Reporting.Group.New == "Snettisham" ~ "Other",
      Reporting.Group.New == "Juneau Mainland" ~ "Other",
      Reporting.Group.New == "Taku River/Stikine Mainstem" ~ "Other",
      Reporting.Group.New == "Chilkat Mainstem" ~ "ChilkatMainstem",
      Reporting.Group.New == "Chilkat Lake" ~ "ChilkatLake",
      TRUE ~ as.character(Reporting.Group.New)
    )
  ) # changing all unnecessary groups to "Others" for MAGMA

loci <- LocusControl$locusnames # should be 48 loci from above

OrderedPops <- groups4_pops239$SILLY

pooled.gcls <- paste(groups4_pops239$SILLY, ".gcl", sep = "")
```


```{r create_baseline, echo = FASLSE}
# get updated silly list from the new inseason -created baseline...
load_sillys("../../Lynn Canal Inseason/2018/Baseline genotpyes/")

# Dput baseline sillys
invisible( sapply( OrderedPops, function(silly) {
  dput(
    x = get( paste( silly, ".gcl", sep = '')),
    file = paste(
      "../2018/baseline/" ,
      silly,
      ".txt",
      sep = ''
    )
  )
}))

search()
detach(pos = 2)

sapply( OrderedPops, function(silly) {
  assign(
    x = paste(silly, ".gcl", sep = ""),
    value = dget(
      file = paste(
        "../2018/baseline/",
        silly,
        ".txt",
        sep = ""
      )
    ),
    pos = 1
  )
})


loci2remove <-
  c("One_Cytb_26",
    "One_CO1",
    "One_Cytb_17",
    "One_c3-98",
    "One_GPDH",
    "One_MHC2_251")

loci <-
  LocusControl$locusnames[!LocusControl$locusnames %in% loci2remove]
```


```{r cleanup}
#removing anything not required for MAGMA
rm(username)
rm(.password)

rm(list = ls(pattern = ".GCL"))

rm(groups4_pops239)
rm(groups7_pops239)

#the final total list of objects in this workspace includes: loci, LocusControl, OrderedPops, and 239 baseline .gcls 01/22/2019
save.image("../2018/MAGMA/data/baseline.RData")
```

